---
title: "index.Rmd"
author: "AF-4"
date: "5/22/2020"
output: html_document
---

```{r setup, include=FALSE}
literacy_rate_data <- read.csv("data/regional-agg_LiteracyRate.csv", stringsAsFactors = FALSE)
library("knitr")
source("scripts/summary_info.R")
source("scripts/agg_table.R")
source("scripts/bar_chart.R")
source("scripts/scatter_plot.R")
source("scripts/map_chart.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Summary Info

Our dataset displays the literacy rates of `r sum_inform(literacy_rate_data)$num_countries` countries around the world. The countries with the hightest total literacy rates were `r sum_inform(literacy_rate_data)$country_highest_total_rate`. The country with the lowest total literacy rate of `r sum_inform(literacy_rate_data)$lowest_total_rate` percent was `r sum_inform(literacy_rate_data)$country_lowest_total_rate`. The average total literacy rate was `r sum_inform(literacy_rate_data)$avg_total_rate`. Also, there were `r sum_inform(literacy_rate_data)$num_least_developed_countries` countries that were considered the least developed.

## Table
```{r echo = FALSE}
kable(agg_table(literacy_rate_data))
```

## Charts
```{r echo = FALSE}
bar_chart(literacy_rate_data)
```

```{r echo = FALSE}
scatter_plot(literacy_rate_data)
```

```{r echo=FALSE}
map_chart(literacy_rate_data)
```
